---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BiometryTraining

```{r, echo = FALSE}
description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
min.r <- substr(description[,"Depends"], 7, 11)
```

<!-- badges: start -->
[![Project Status: Active:  The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Codecov test coverage](https://codecov.io/gh/biometryhub/BiometryTraining/branch/master/graph/badge.svg)](https://codecov.io/gh/biometryhub/BiometryTraining?branch=master)
[![R build status](https://github.com/biometryhub/BiometryTraining/workflows/R-CMD-check/badge.svg)](https://github.com/biometryhub/BiometryTraining/actions)
![pkgdown](https://github.com/biometryhub/BiometryTraining/workflows/pkgdown/badge.svg)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r min.r`-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r gsub('-', '--', version)`-orange.svg?style=flat-square)](/commits/master)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
<!-- badges: end -->

The goal of BiometryTraining is to provide functions to aid in the Design and Analysis of Agronomic-style experiments through easy access to documentation and helper functions, especially while teaching these concepts.

## Installation

You can install the latest version of BiometryTraining from [GitHub](https://github.com/) with:

```{r eval=F}
if(!require("devtools")) install.packages("devtools") 
devtools::install_github("biometryhub/BiometryTraining", upgrade = FALSE)
```

Load the package and start using it with:

```{r eval=F}
library(BiometryTraining)
```

